---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

I am choosing to analyze trends within this dataset such as how the most checked out book of the year can change in the future. The first chart will give information on different years and what the top book was for the corresponding year. I also chose to analyze and compare the success of ebooks versus other books such as physical copies, which can be seen in the second chart. This was mostly interesting for me because I was able to interpret a trend in which ebooks gain popularity over time. The third chart that I create also relates to the type of book that is checked out, however, there is less emphasis on whether or not the book is online. So this analysis considers all of the material types, and explores popularity within these subgroups.

### Summary Information

From working on the Summary information, I was able to discover basic information about the Seattle Public Library dataset. I found that the number of checkouts for ebooks has experienced an increasing trend. I have also uncovered the average number of checkouts for both ebooks, and regular physical books. The most popular types of material that have been checked out by users start at physical books, progress to ebooks, and then continue on to audio books.

### The Dataset

- Who collected/published the data?  
  The Seattle Public Library
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
  Parameters: CheckoutType, MaterialType, UsageClass, CheckoutYear, CheckoutMonth, Title, ISBN, Creator, Publisher, Subjects, and more.
- How was the data collected or generated?  
  The data was generated by keeping track of past sources regarding library information. For information on digital items of the SPL, data is generated through FBDigital, and other sources alike.
- Why was the data collected?  
  The data was collected in order to provide evidence for trends that the library should consider. This can help them improve their ability to serve the Seattle community.
- What, if any, ethical questions do you need to consider when working with this data?  
  Ethical questions that should be considered include how some of the trends listed within the data may be fabricated information. This could be done in order to paint the library in a better light.
- What are possible limitations or problems with this data?   (at least 200 words)
  Limitations with this data is that it does not keep track of the people who check out these items from the library. If this data is used to find trends in the library information, it may leave out other important information regarding who is involved.


### First Trends Over Time Chart

This chart shows how the top book that is checked out within a year can change over time. It tracks the most checked out book for each year and shows that data within the plot. This can be used by the Seattle Public Library by giving more insight into what books are successful within the community.

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1.R")}
```

### Second Trends Over Time Chart

Chart 2 compares the overall success of ebooks when compared to the total books checked out. The number of checkouts for ebooks can serve as a checkpoint for the library,in which they can track the trend of using physical books versus online books. This can be very useful for tracking future trends as technology progresses.

``````{r, echo = FALSE, code = readLines("chart2.R")}
```

### Your Choice

This chart includes analyzing the different types of books that were checked out from the Seattle Public Library. Through this chart. The data can be used to provide insight to the library of ways in which their service can progress. This can be done by assimilating to the consumer trends.
``````{r, echo = FALSE, code = readLines("chart3.R")}
```


